\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-02-15 doc/USER_MANUAL/manual_SPECFEM3D.tex
added DG references to the manual

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08}.
It is also very well suited to parallel implementation on very large supercomputers \citep{KoTr02a,KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10} as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}. Tensor products inside each element can be optimized to reach very high efficiency \citep{DeFiMu02}, and mesh point and element numbering can be optimized to reduce processor cache misses and improve cache reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D) or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06} as well as mixed meshes, although with increased cost and reduced accuracy in these elements, as in the discontinuous Galerkin method.\\

Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies, in which very high frequencies need to be modeled near the fault, see e.g. \cite{PuAmKa09})
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09}.\\

>>>>

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08}.
The spectral element approach admits spectral rates of convergence and allows exploiting $hp$-convergence schemes.
It is also very well suited to parallel implementation on very large supercomputers \citep{KoTr02a,KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10} as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}. Tensor products inside each element can be optimized to reach very high efficiency \citep{DeFiMu02}, and mesh point and element numbering can be optimized to reduce processor cache misses and improve cache reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D) or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06} as well as mixed meshes, although with increased cost and reduced accuracy in these elements, as in the discontinuous Galerkin method.\\

Note that in most geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies, in which very high frequencies or supershear rupture need to be modeled near the fault, see e.g. \cite{BeGlCrViPi07,BeGlCrVi09,PuAmKa09,TaCrEtViBeSa10})
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient;
conforming mesh doubling bricks can efficiently handle mesh size variations \citep{KoTr02a,KoLiTrSuStSh04,LeChLiKoHuTr08,LeChKoHuTr09,LeKoHuTr09}.
Also, without significant modifications in the complexity of the
discontinuous technique \citep{CaKaBr10,SmCoObOvSch10},
usually those methods need to assume constant material properties inside
each element, while the SEM can handle gradients inside each element.\\
